### 2021-01-16 paper/localpsf.tex
more edits

\begin{defn}
	\label{defn:alpha_rho_mu_sigma}
	We define the spatially varying volume, $\alpha$, the scaled impulse response, $\rho_x$, the spatially varying mean, $\mu$, and the spatially varying covariance, $\Sigma$, as follows:
	\begin{align*}
	\alpha:\Omega \rightarrow \mathbb{R}, &\qquad \alpha(x) := \int_{\Omega} \phi_x(z) dz, \\
	\rho_x:\Omega \rightarrow \mathbb{R}, &\qquad \rho_x := \phi_x \big/ \alpha(x), \\
	\mu:\Omega \rightarrow \mathbb{R}^d, &\qquad \mu(x) := \int_\Omega z \rho_x(z) dz, \\
	\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d}, &\qquad\Sigma(x) := \int_\Omega (z - \mu(x))(z - \mu(x))^T \rho_x(z) dz.
	\end{align*}
\end{defn}

>>>>

\begin{defn}
	\label{defn:alpha_rho_mu_sigma}
	We define the spatially scaling factor, $\alpha$, the scaled impulse response, $\rho_x$, the spatially varying mean, $\mu$, and the spatially varying covariance, $\Sigma$, as follows:
	\begin{align*}
	\alpha:\Omega \rightarrow \mathbb{R}, &\qquad \alpha(x) := \int_{\Omega} \phi_x(z) dz, \\
	\rho_x:\Omega \rightarrow \mathbb{R}, &\qquad \rho_x := \phi_x \big/ \alpha(x), \\
	\mu:\Omega \rightarrow \mathbb{R}^d, &\qquad \mu(x) := \int_\Omega z \rho_x(z) dz, \\
	\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d}, &\qquad\Sigma(x) := \int_\Omega (z - \mu(x))(z - \mu(x))^T \rho_x(z) dz.
	\end{align*}
\end{defn}
